\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2022-04-13 sections/results.tex
Change: Update default pipeline section of Results

  The systematic analyses performed in the previous sections clearly show that the choice of tools and parameters can have a big impact on the final co-occurrence network. For some of these choices (e.g. \ac{dada2} vs. deblur) there is no clear metric to establish a best protocol.
  For other choices, the mock communities provide an opportunity to select combination of parameters that yield more accurate and robust results.
  Despite this partial degree of assessment, we wish to suggest a combination of tools and parameters that produce networks that are derived from the combination of tools which performed best on the mock communities, and displayed highest robustness to switching to alternative methods.
  These tools and parameters are chosen as the defaults for the pipeline and are given in Table~\ref{tab:default_options}.

  The recommended tool for the \ac{dc} step (\ac{dada2}) was chosen based on their accuracy in recapitulating the reference sequences in mock communities and synthetic data.
  The choice of the taxonomy reference database in the \ac{ta} step is dictated largely by the species expected to be present in the sample as well the database used in similar studies if comparison is a goal.
  Nevertheless, we suggest \ac{gg} database along with the NaiveBayes classifier as the query tool since the database is used most often in taxonomic studies.
  % TODO: Default OP step values and references
  The abundance threshold at the \ac{op} step is set at ... because ....
  Finally, we make use of the consensus methods developed in this paper ... on the networks generated using \ac{mldm}, \ac{spieceasi} and \ac{sparcc} to obtain a final consensus network in the \ac{ni} step.

  Figure~\ref{fig:figure6}A shows the default network compared against networks generated by altering one of the steps of the pipeline from the default.
  These results indicate that the biggest differences in networks occur when the reference database or the network inference algorithm are changed.
  Furthermore, the L1 distance of networks generated by altering one of the steps of the pipeline from the default against the default network (Figure~\ref{fig:figure6}B) shows that the biggest deviations from the default network occur when the \ac{ta} and \ac{ni} steps are changed, reinforcing the same results observed in Figure~\ref{fig:figure2}. Figure~\ref{fig:figure7} shows the co-occurrence networks inferred for the hard palate for healthy subjects in a periodontal disease study~\cite{Chen2018} and the healthy stool microbiome in fecal microbial transplant study~\cite{Kang2017}. These consensus networks were generated using the default tools and parameters from Table~\ref{tab:default_options}.

>>>>

  The systematic analyses performed in the previous sections clearly show that the choice of tools and parameters can have a big impact on the final co-occurrence network.
  For some of these choices (e.g. \ac{dada2} vs. Deblur) there is no clear metric to establish a best protocol.
  For other choices, the mock communities and synthetic data provide an opportunity to select combination of tools that yield more accurate and robust results.
  Despite this partial degree of assessment, we wish to suggest a combination of tools and parameters that produce networks that are derived from the combination of tools which performed best on the mock communities, and displayed highest robustness to switching to alternative methods.
  These tools and parameters are chosen as the defaults for the pipeline and are given in Table~\ref{tab:default_options}.

  The recommended tool for the \ac{dc} step (\ac{dada2}) was chosen based on its accuracy in recapitulating the reference sequences in mock communities.
  For the chimera checking module of the \ac{dc} step, both uchime and remove bimera perform similarly, we suggest using remove bimera since it was developed specifically for \ac{dada2} and should provide the best performance for that denoising method.
  The choice of the taxonomy reference database in the \ac{ta} step is dictated largely by the species expected to be present in the sample as well the database used in similar studies, if comparison is a goal.
  Nevertheless, we suggest \ac{gg} database along with the NaiveBayes classifier as the query tool since the database is used most often in taxonomic studies.
  % TODO: Default OP step values and references
  The abundance threshold at the \ac{op} step is set at ... because ....
  For the \ac{op} step, we recommend that the filtering be turned on and used at the default settings, unless a taxonomy entity of interest might be filtered out at the default settings.
  This is necessary since a large number of rows in the counts matrix would reduce the accuracy of the inference methods and increase the computational time.
  Finally for the \ac{ni}, we recommend the scaled-sum consensus method along with p-value merging (for the correlation-based methods) to generate a final consensus network for the input data.

  Figure~\ref{fig:figure7}A shows the default network compared against networks generated by altering one of the steps of the pipeline from the default.
  These results indicate that the biggest rewiring in networks occur when the reference database or the network inference algorithm are changed.
  % TODO: Show proof??
  The filtering in the \ac{OP} step when turned off also adds a large number of new nodes, but the edges between the common nodes (with the default network) are fairly conserved.
  % TODO: Finalize this figure
  Furthermore, the L1 distance of networks generated by altering one of the steps of the pipeline from the default against the default network (Figure~\ref{fig:figure7}B) shows that the biggest deviations from the default network occur when the \ac{ta} and \ac{ni} steps are changed, reinforcing the same results observed in Figure~\ref{fig:figure2}.
  Figure~\ref{fig:figure7} shows the co-occurrence networks inferred for the healthy subjects (control) and autistic subjects in the fecal microbiome transplant study~\cite{Kang2017}.
  These consensus networks were generated using the default tools and parameters from Table~\ref{tab:default_options}.
